\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-28 paper.tex
initial round of edits

We would also like to thank Inoue Hikaru for his help with translations and
researching AR technology. A special thank you to the IQP team working with
Kyoto VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
filming and editing the app trailer.

@@

We built, tested and polished a mobile app to deliver an audio tour,
incorporating various AR features to enhance the experience. In this app, which
we call ARuko, many of the AR features were aimed at improving accessibility.
These features included translating signs and providing additional info on the
physical map located at the site. Other features were purely for spectacle,
such as the ability to take an AR `souvenir' home by pointing the camera at the
ticket.

ARuko went through multiple iterations of user testing and bug testing at the
site of the audio tour, Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
\ref{sec:finalFieldTesting} go into detail about our two days of field testing
on-site. From these tests, we were able to refine the user experience, and
identify important features to add to the app. Much of the app's and
functionality was dictated by Atticus Sims of Kyoto VR, who plans to monetize
the app. We also worked closely with the IQP team, who has been tasked with
exploring funding options and creating promotional content.

Since our app had to deliver an audio tour supplemented by images based on your
GPS position, we developed an internal tool to design these regions. Editour
provides a rich editing suite for designing tours with images and audio.
Section~\ref{sec:editingATour} goes into detail about the features of this web
app. We also wrote a backend to manage the tour files, allowing one of us (or
our sponsor, Atticus Sims) to download a zip file containing all of the media
and info to reconstruct the tour. This zip can be extracted into the Unity
project, which reconstructs the tour from the downloaded contents. We were able
to host the backend on the server provided by Kyoto VR's hosting plan; we
discuss the hurdles that we overcame to deploy the Editour backend with Kyoto
VR's current setup in Section~\ref{sec:deployingTheEditourBackend}.

At the end of this paper, we also discuss the alternative AR app concepts that
were explored before development became completely focused on the tour app
ARuko.

@@

The field of consumer-oriented Augmented Reality (AR) technology is just coming
into full swing, and it presents many unique opportunities for a myriad of
fields. This budding technological platform uses digital displays to augment
real-world information with computer-generated data. As the technology
progresses several disparate industries have found novel uses for it, some
becoming extremely profitable~\autocite{webster2018}. With smartphone
manufacturers investing billions into AR technology~\autocite{mason2016}, it
seems poised to be the next big digital interface.

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. AR technology can provide accessible
information to tourists and art viewers that they would not be able to get any
other way. Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example
of this~\autocite{bornoff2000}. Kinkaku-ji is a UNESCO World Heritage
Site~\autocite{unesco} and one of the most popular tourist destinations in
Japan~\autocite{japanguide2019}. The Golden Pavilion is a magnificent sight to
behold, but the gardens and grounds are the true beauty of Kinkaku-ji. It is a
living masterpiece of Zen Buddhist landscape design, expanding on the natural
beauty of Kyoto's forests and mountains through the practice of borrowed
scenery~\autocite{kuitert2002}.

@@

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
and ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. The experience of walking through the site is enhanced by
informative narration and AR pop-ups that do not alter the buildings or ground
in real life.

@@

Augmented Reality, or AR, is a type of human-computer interface where
perceptions of the real world are enhanced by computer-generated information.
This differs from Virtual Reality (VR) in that a VR experience consists
exclusively of virtual information. In AR, virtual information is mixed with
sensory input from the real world~\autocite{carmigniani2011}. This can enhance
the user's perception of reality by providing information that would be
difficult or impossible to display through traditional means.

For example, AR can be used to display information about historical events,
places, and objects overlaid onto images of the real
world~\autocite{saenz2009}.  This provides the user with useful information
without needing to alter the real historic site.

@@

While preparing for this project our team researched the current state of
augmented reality technology. Smartphones are the most commonly used AR hardware
by far~\autocite{boland2018}. Typically smartphone AR applications make use of
the phone's camera, accelerometer, gyroscope, and GPS sensors to reproduce a
view of the real world with virtual information layered on top of
it~\autocite{bonsor2018}.

@@

Even though it is still a developing technology, augmented reality has been used
in many disparate disciplines, including data
visualization~\autocite{resnick2017}, commerce~\autocite{matney2018},
marketing~\autocite{sharma2015}, education~\autocite{stewart-smith2012}, visual
art~\autocite{katz2018}, and even archaeology~\autocite{eve2012}.

@@

As previously discussed, AR is a new and growing field full of opportunities.
But of course, as with anything new, our understanding of AR and how to develop
for it is limited.  And with those limitations come challenges. All sorts of
different challenges and limitations face the development and production of AR
apps. Here are some that we considered when working on our app.

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. This means a few different things. For starters, many AR
apps and features available on smartphones offer very little in the way of
functionality or practicality; quite simply, they are primarily used for minor
spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one of
the most popular apps to use AR, \textit{Pokémon Go}, primarily uses its AR
feature to place a Pokémon in the world around you through your phone camera for
you to capture. But when it is in the world, it does not interact with anything
around it. It just floats a fixed distance away from you, simply placed on top
of your camera's video feed.

Additionally, in many cases where AR is used, the task could be accomplished as
well or better without AR~\autocite{theappsolutions2018}. Returning to the
\textit{Pokémon Go} example, when the AR feature is left on while capturing a
Pokémon, the extra power needed for this feature drains the device faster, makes
it harder to hit the Pokémon with a Pokéball due to the model drifting in the
environment, and can even slow app performance, all of which detract from the
ability to play and enjoy the game.

One of the major problems facing AR development as a whole, and one that we ran
into as well, is limited hardware. For starters, smartphone cameras present a
major limitation. Many smartphone cameras only capture images in 2D, which can
make generating AR content in a 3D world difficult without the use of QR or
barcode markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on
smartphones can also be too imprecise for good AR
tracking~\autocite{geospatialworld2018}.

The biggest hardware limitation comes from which platform to use. AR apps are
most commonly designed for smartphones due to their relatively low cost and how
accessible they are. But, as we just discussed, smartphones come with a host of
hardware limitations that make achieving satisfying AR capabilities difficult.
Additionally, AR apps for smartphones tend not to be very user-friendly, and
oftentimes even complicate the task or activity they were meant to
enhance~\autocite{theappsolutions2018}.  The alternative then is to turn to
dedicated hardware, like Microsoft's HoloLens.  But dedicated hardware like the
HoloLens is very inaccessible and expensive; Microsoft only offers developer
editions of the HoloLens, and for the incredibly steep price of
\$3,500~\autocite{microsoft2019}.

The challenges we faced during development mirrored these that plague the
industry as a whole very accurately. We struggled with how exactly we would us
AR for our app in a way that benefit the experience as a whole, but believe the
way we've implemented it will enhance the user's experience. Hardware issues
were definitely our biggest challenge.  Only one of our phones is new enough to
run AR technology at a decent level, making testing of our application
difficult.

@@

Before our project started, Kyoto VR was already using an app with a limited
form of AR for tours. The app, called izi.TRAVEL, allows users to create audio
tours with audio and image files tied to specific locations in the real
world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
aimed at museums and city tours~\autocite{izitravel} but can be used for tours
of historic sites too.  Kyoto VR used the platform to make an audio tour of
Kinkaku-ji, one of the most popular tourist destinations in
Japan~\autocite{bornoff2000} and an important historic heritage
site~\autocite{unesco}.

@@

By using GPS data from the user's phone to play audio and display images at
specific places in the real world izi.TRAVEL uses a limited form of augmented
reality. Our group aimed to implement and extend this functionality in our own
app. See Section \ref{sec:aruko} for more details.

@@

Before we could start working on creating our app, we first needed to decide
which AR development platform to use. Our preliminary research had shown us that
there are so many different platforms out there, all of which have been used to
create great AR apps. There were a lot of things we needed to consider before
finalizing on a platform, like what features it offered, which devices and
operating systems the app could run on, and definitely the cost. Detailed below
are some of the different platforms we considered.

@@

ARKit and ARCore are both AR frameworks that enable apps to take advantage of
powerful AR related features. ARKit is developed by Apple and can only be used
by iPhones. Google's ARCore framework can deploy to both Android and iPhone.
Many cross platform solutions will leverage the full potential of their target
platform by using either ARKit or ARCore ``under the hood''. Both ViroReact and
Vuforia use ARKit or ARCore depending on the target platform
\autocites{vuforiaFusion}{moon2018}.

ARKit 3 aims to support a wide array of new features and will be available in
iOS 13. Notably, one of these features is ``people occlusion,'' which will allow
virtual objects to be realistically obscured when someone walks in front of the
object~\autocite{apple2019}. This kind of technology could be useful for us
since our app uses AR in crowded places.  As of August 2019, this feature is
not on the horizon for Google's Android AR framework, ARCore.

Both ARKit and ARCore have well-supported APIs for Unity. ARKit 3 support is
coming to Unity, along with all of the advanced features that it
brings~\autocite{stinson2019}.

@@

Wikitude is another major AR development kit that is very prevalent in the
world of AR development. It has over 130,000 registered AR developers, and is
powering over 30,000 AR apps across smartphones, tablets, and smart
glasses~\autocite{wikitude2018}.  And it's easy to understand why Wikitude has
so many registered developers when you see the list of features it offers. Some
of the features that appealed most to us were their Instant Tracking, allowing
for augmentation using flat surfaces; Image Tracking, allowing for augmentation
using one or multiple 2D images; and Geo AR, allowing for creation of
geo-markers at specific locations to triggered AR
content~\autocite{wikitude2018}.

Wikitude also supports all sorts of different platforms. It supports Android,
Apple, and Windows phones and tablets, as well as smart glasses like the Epson
Moverio, Microsoft Hololens, and Vuzix smart glasses~\autocite{wikitude2018}.
Additionally, many different development frameworks are capable of running
Wikitude's SDK.  According to Wikitude's website, their SDK works with Windows,
Android, and iOS development frameworks, as well as ARCore and ARKit, Flutter,
Cordova, Xamarin, and even Unity~\autocite{wikitude2018}.

From all of this information, Wikitude certainly sounds like a fantastic AR
development platform; it certainly did to us. But the issue we ran into was the
cost. Wikitude is, in fact, free for eligible startups, but given the criteria
they list on their site, we were not confident that we would qualify. Aside
from this option, Wikitude offers a 30-day demo license for \euro{499}, which
is a lot for use to pay for a license that would not even last for our entire
project. They also charge \euro{1990} for their SDK Pro, and \euro{2490} for
their SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very
limited budget, we knew that we would have to pass on Wikitude and choose a
different AR development platform.

@@

The company motive.io used to work on a product that would allow users to create
an engaging AR experience in the style of \textit{Pokémon Go}. Their service
would have purportedly handled technical details such as hosting, storage, and
user accounts. The promotional video shows the creation of a location-based AR
game where the user pretends to hack into ATMs using the real-world locations of
ATMs in a city\autocite{odom2017}.

Unfortunately, it appears that the company has completely pivoted off of this
idea, and has since moved to AR training software\autocite{motiveio}.

We reached out to motive.io via email for any advice they might be willing to
give us, but we received no response.

\subsubsection{Viro AR}
\label{sec:viroAR}

Viro AR comes in two flavors: ViroReact and ViroCore. ViroCore allows
developers to build an AR Application with Java. The disadvantage of this is
that ViroCore only allows developers to target Android, which unfortunately
made ViroCore not an option for our project. ViroReact is the cross-platform
option for ViroAR. ViroReact leverages the cross-platform capabilities of
React, which is Facebook's JavaScript Library for developing user
interfaces~\autocite{facebook2019}.

Since our project is not a game, we initially wanted to avoid using a
fully-featured game engine. Therefore, we decided to take the time to explore
this framework since it appeared to be more tailored to our specific use case.
Viro Media also recognizes that all developers who wish to create an app with
3D capabilities are not necessarily game developers. Viro Media pitches Viro
AR as ``The perfect alternative to specialized game engines, ViroAR is a
platform for rapidly building ARKit and ARCore apps. Our platform allows
developers to focus on what they do best by leveraging familiar tools and
frameworks used in mobile application development''~\autocite{viro2019}.
While the majority of our team has decent experience with writing JavaScript,
we all either have very little or no experience writing React apps.

In most development scenarios, every time you wish to test your app on actual
hardware, you must first compile your app using either Xcode or Android Studio
depending on your platform. Once you have built the app, your device needs to
install the app. This process can be very time consuming, especially since
frequent tests on real hardware is important for something as intensive as
AR.

An alternative to building your app is to run your app through an emulator on
the computer you are using for development.

According to Techopedia, ``Emulation is the process of imitating a
hardware/software program/platform on another program or platform. This makes
it possible to run programs on systems not designed for
them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
up development. Loading programs onto the Android emulator usually much faster
than installing the APK onto the actual device. Additionally, you can mock
almost all of the important features of an actual Android device, including
calls, text, GPS position, device rotation and more~\autocite{androidemulator}.

@@

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way to
successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The moral is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone hardware to the limit, emulation is not something is
not something we wanted to struggle with. On top of this, our testing required
us to move the camera through the world at various speeds and angles, which is
simply cumbersome with a laptop webcam.

>>>>

We would also like to thank Inoue Hikaru for his help with translations and
researching AR technology. A special thank you to the IQP team working with
Kyoto VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
filming and editing the app trailer, as well as providing help with testing.

@@

Our team built, tested and polished a mobile app to deliver an audio tour,
incorporating various augmented reality (AR) features to enhance the
experience. Our app delivers a tour of Kinkaku-ji, or The Temple of the Golden
Pavilion, a popular tourist destination in Kyoto. In this app, which we call
ARuko, many of the AR features were aimed at improving accessibility. These
features include translating signs and providing additional info on the
physical map located at the site. Other features were purely for spectacle,
such as the ability to take an AR ``souvenir'' home by scanning the ticket
to enter Kinkaku-ji.

ARuko went through multiple iterations of user testing and bug testing at
Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
\ref{sec:finalFieldTesting} go into detail about our two days of field testing
on-site. From these tests, we were able to refine the user experience, and
identify important features to add to the app. Much of the app's functionality
was dictated by Atticus Sims, C.E.O and founder of Kyoto VR, who plans to
monetize the app. We also worked with an IQP team, who had been tasked with
exploring funding options and creating promotional content.

Since our app had to deliver an audio tour supplemented by images based on your
latitude and longitude, we developed an internal tool to design physical
regions for each step of the tour. This tool, called Editour provides a rich
editing suite through a simple web interface. Section~\ref{sec:editingATour}
goes into detail about the features of this web app. We also wrote a backend to
manage the tour files, allowing one of us (or our sponsor, Atticus Sims) to
download a zip file containing all of the media and info to reconstruct the
tour. This zip can be extracted into the source files for ARuko, which rebuilds
the tour from the downloaded contents. We were able to host the backend on the
server provided by Kyoto VR's hosting plan; we discuss the hurdles that we
overcame to deploy the Editour backend with Kyoto VR's current setup in
Section~\ref{sec:deployingTheEditourBackend}.

In Section~\ref{sec:alternativeArAppConcepts}, we also discuss the alternative
AR app concepts that were explored before development became completely focused
on ARuko.

@@

The field of consumer-oriented augmented reality (AR) technology is just coming
into full swing, and it presents many unique opportunities for a myriad of
fields. This budding technological platform uses digital displays to augment
real-world information with computer-generated data. As the technology
progresses, several disparate industries have found novel uses for it, some
becoming extremely profitable~\autocite{webster2018}. With smartphone
manufacturers investing billions into AR technology~\autocite{mason2016}, it
seems poised to be the next big digital interface.

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. This technology can provide
accessible information to tourists and art viewers that they would not be able
to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto, is the
perfect example of a site that would benefit from AR~\autocite{bornoff2000}.
Kinkaku-ji is a UNESCO World Heritage Site~\autocite{unesco} and one of the
most popular tourist destinations in Japan~\autocite{japanguide2019}. The
Golden Pavilion is a magnificent sight to behold, but the gardens and grounds
are the true beauty of Kinkaku-ji. It is a living masterpiece of Zen Buddhist
landscape design, expanding on the natural beauty of Kyoto's forests and
mountains through the practice of borrowed scenery~\autocite{kuitert2002}.

@@

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. The experience of walking through the site is enhanced by
informative narration and AR pop-ups that do not alter the buildings or ground
in real life.

@@

Augmented reality, or AR, is a type of human-computer interface where
perceptions of the real world are enhanced by computer-generated information.
This differs from virtual reality (VR) in that a VR experience consists
exclusively of virtual information. In AR, virtual information is mixed with
sensory input from the real world~\autocite{carmigniani2011}. This can enhance
the user's perception of reality by providing information that would be
difficult or impossible to display through traditional means.

For example, AR can be used to display information about historical events,
places, and objects overlaid onto images of the real
world~\autocite{saenz2009}.  This provides the user with useful information
without needing to alter a real historic site.

@@

While preparing for this project our team researched the current state of AR
technology. Smartphones are the most commonly used AR hardware by
far~\autocite{boland2018}. Typically smartphone AR applications make use of the
phone's camera, accelerometer, gyroscope, and GPS sensors to reproduce a view
of the real world with virtual information layered on top of
it~\autocite{bonsor2018}.

@@

Even though it is still a developing technology, AR has been used in many
disparate disciplines, including data visualization~\autocite{resnick2017},
commerce~\autocite{matney2018}, marketing~\autocite{sharma2015},
education~\autocite{stewart-smith2012}, visual art~\autocite{katz2018}, and
even archaeology~\autocite{eve2012}.

@@

Many of the existing applications using AR, in our eyes, do not leverage the
full potential of this emerging technology. As with any new field, our
understanding of AR and how to develop for it is limited. All sorts of
different challenges and limitations face the development and production of AR
apps. Here are some that we considered when working on our app.

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. Many AR apps and features available on smartphones offer
very little in the way of functionality or practicality; quite simply, they are
primarily used for minor spectacles and simple
tricks~\autocite{theappsolutions2018}. For example, one of the most popular
apps to use AR, \textit{Pokémon Go}, primarily uses its AR feature to place a
Pokémon on top of a camera's video feed. Disappointingly, it does not interact
with anything around it. It just floats a fixed distance away from the user.

Additionally, in many cases where AR is used, the task could be accomplished as
well or better without AR~\autocite{theappsolutions2018}. Returning to the
\textit{Pokémon Go} example, when the AR feature is left on while capturing a
Pokémon, the extra power needed for this feature drains the device's battery
faster. Also, it makes it harder to hit the Pokémon with a Pokéball due to the
model drifting in the environment. On top of all of this, the performance of
the app suffers drastically, especially on older devices. All of these problems
detract from the ability to play and enjoy the game.

One of the major problems facing AR development as a whole---including our
project---is limited hardware. For starters, smartphone cameras present a
major limitation. Many smartphone cameras only capture images in 2D, which can
make generating AR content in a 3D world difficult without the use of QR or
barcode markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on
smartphones can also be too imprecise for good AR
tracking~\autocite{geospatialworld2018}.

AR apps are most commonly designed for smartphones due to their relatively low
cost and how accessible they are. However, smartphones come with a host of
hardware limitations that make achieving satisfying AR capabilities difficult.
Additionally, AR apps for smartphones tend not to be very user-friendly, and
oftentimes even complicate the task or activity they were meant to
enhance~\autocite{theappsolutions2018}.  The alternative then is to turn to
dedicated hardware, like Microsoft's HoloLens. The issue is that dedicated
hardware like the HoloLens is very inaccessible and expensive; Microsoft only
offers developer editions of the HoloLens, and for the incredibly steep price
of \$3,500~\autocite{microsoft2019}.

The challenges we faced during development mirrored those that plague the
industry as a whole very accurately. We struggled with how exactly we would use
AR for our app in a way that benefited the experience as a whole. Despite our
initial apprehension, we believe the way we have integrated AR into our app
enhances the user experience. Hardware issues were definitely our biggest
challenge. Only one member of our team had a phone new enough to run AR technology at a
decent level, making testing of our application difficult.

@@

Before our project started, Kyoto VR was already using an app to deliver audio
tours. The app, called izi.TRAVEL, allows users to create audio tours with
audio and image files tied to specific locations in the real
world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
aimed at museums and city tours~\autocite{izitravel} but can be used for tours
of historic sites too.  Kyoto VR used the platform to make a simple audio tour
of Kinkaku-ji.

@@

Our group aimed to implement all the functionality of izi.TRAVEL and more in
our own app. See Section \ref{sec:aruko} for more details.

@@

Before we could start working on creating our app, we first needed to decide
which AR development platform to use. Based on our preliminary research, we
learned there are many powerful platforms available. There were many things we
needed to consider before deciding on a platform. These considerations included
what features the platform offered, which devices and operating systems the app
could run on, and the cost. Detailed below are some of the different platforms
we considered.

@@

ARKit and ARCore are both frameworks that enable apps to take advantage of
powerful AR related features. ARKit is developed by Apple and can only be used
by iPhones~\autocite{summerson2018}. Google's ARCore framework can deploy to both
Android and iPhone. Many cross platform solutions will leverage the full
potential of their target platform by using either ARKit or ARCore ``under the
hood.'' Both ViroReact and Vuforia use ARKit or ARCore depending on the target
platform \autocites{vuforiaFusion}{moon2018}.

ARKit 3 aims to support a wide array of new features and will be available in
iOS 13~\autocite{apple2019}. Notably, one of these features is ``people
occlusion,'' which will allow virtual objects to be realistically obscured when
someone walks in front of the object. This kind of technology could be useful
for us since our app uses AR in crowded places.  As of August 2019, this
feature is not on the horizon for ARCore.

Both ARKit and ARCore have well-supported APIs for Unity. ARKit 3 support is
coming soon to Unity, along with all of the advanced features that it
brings~\autocite{stinson2019}.

@@

Wikitude is another major AR development kit that is very prevalent in the
world of AR development. It has over 130,000 registered AR developers, and is
powering over 30,000 AR apps across smartphones, tablets, and smart
glasses~\autocite{wikitude2018}. It is easy to understand why Wikitude has so
many registered developers considering the list of features the platform
offers. Some of the features that appealed most to us were their ``Instant
Tracking,'' allowing for augmentation using flat surfaces; ``Image Tracking,''
allowing for augmentation using one or multiple 2D images; and ``Geo AR,''
allowing for creation of geo-markers at specific locations to trigger AR
content.

Wikitude supports Android, Apple, and Windows phones and tablets, as well as
smart glasses like the Epson Moverio, Microsoft HoloLens, and Vuzix smart
glasses. Additionally, many different development frameworks are capable of
running Wikitude's software development kit (SDK). According to Wikitude's
website, their SDK works with Windows, Android, and iOS development frameworks,
as well as ARCore and ARKit, Flutter, Cordova, Xamarin, and even Unity.

Based on this information, Wikitude was initially appealing to us. However, the
cost was a major issue. Wikitude is free for eligible startups, but given the
criteria they list on their site, we were not confident that we would qualify.
Aside from this option, Wikitude offers a 30-day demo license for \euro{499},
which was far beyond the resources available to us. They also charge
\euro{1990} for their SDK Pro, and \euro{2490} for their SDK Pro 3D. Given
these prices, and our very limited budget, we decided to consider other
options.

@@

The company motive.io previously was developing a product that would allow
users to create an engaging AR experience in the style of
\textit{Pokémon~Go}~\autocite{odom2017}. Their service would have purportedly
handled technical details such as hosting, storage, and user accounts. The
promotional video shows the creation of a location-based AR game where the user
pretends to hack into ATMs using the real-world locations of ATMs in a city.

Unfortunately, it appears that the company has completely pivoted off of this
idea, and has since moved to developing AR training
software~\autocite{motiveio}. We reached out to motive.io via email for any
advice they might be willing to give us, but we received no response.

\subsubsection{ViroAR}
\label{sec:viroAR}

Viro AR comes in two flavors: ViroReact and ViroCore\autocite{facebook2019}.
ViroCore allows developers to build an AR Application with Java. The
disadvantage of this is that ViroCore only allows developers to target Android,
which unfortunately made ViroCore not an option for our project. ViroReact is
the cross-platform option for ViroAR. ViroReact leverages the cross-platform
capabilities of React, which is Facebook's JavaScript Library for developing
user interfaces~\autocite{facebook2019}.

Since our project is not a game, we initially wanted to avoid using a
fully-featured game engine such as Unity (see Section~\ref{sec:unity}.
Therefore, we decided to take the time to explore this framework since it
appeared to be more tailored to our specific use case. Viro Media also
recognizes that all developers who wish to create an app with 3D capabilities
are not necessarily game developers. Viro Media pitches ViroAR as ``The
perfect alternative to specialized game engines, ViroAR is a platform for
rapidly building ARKit and ARCore apps. Our platform allows developers to focus
on what they do best by leveraging familiar tools and frameworks used in mobile
application development''~\autocite{viro2019}. While the majority of our team
has decent experience with writing JavaScript, we have have very little experience
writing React apps.

In most app development scenarios, to test the app on actual hardware, it must
be compiled using either Xcode or Android Studio depending on your platform.
Once you have built the app, your device needs to install the app. This process
can be very time consuming, especially when needing to run frequent tests on
the target platform.

An alternative to building an app for a physical phone is to run it through an
emulator on a computer.

According to Techopedia, ``Emulation is the process of imitating a
hardware/software program/platform on another program or platform. This makes
it possible to run programs on systems not designed for
them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
up development. Loading programs onto the Android emulator is usually much
faster than installing an Android package file (APK) onto the actual device.
Additionally, emulators can mock almost all of the important features of an
actual Android device, including calls, text, GPS position, device rotation and
more~\autocite{androidemulator}.

@@

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way
to successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The takeaway is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone hardware to the limit, emulation is not something
is not something we wanted to struggle with. On top of this, our testing
required us to move the camera through the world at various speeds and angles,
which is simply cumbersome with a laptop webcam.
